---
title: "CrabTutorial"
author: "Ethan Savario"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is an R package that focuses on manipulating crab data such as carapce measurements,
latitude found, and color. This package contains functions that allow the user to omit missing values in data, manipulate units of measurement,calculate the carapace area of an object, to create a linear model and plot the linear model on a point graph. 
Crabbers, fishers, and researchers may be interested in this package and in being able to 
graph data regarding crabs, find the relationship between characteristics of a 
crab, and quickly compare measurements using one uniform unit of measurement.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
