---
title: "CrabTutorial"
author: "Ethan Savario"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is an R package that focuses on manipulating crab data such as carapce measurements,
latitude found, and color. This package contains functions that allow the user to omit missing values in data, manipulate units of measurement,calculate the carapace area of an object, to create a linear model and plot the linear model on a point graph. 
Crabbers, fishers, and researchers may be interested in this package and in being able to 
graph data regarding crabs, find the relationship between characteristics of a 
crab, and quickly compare measurements using one uniform unit of measurement.

Below is some sample data reguarding crabs that can be used. This will be downloaded from google sheets:

```{r}
#install.packages("googlesheets4")
library(googlesheets4)
googlesheets4::gs4_deauth()
crab_data<-read_sheet("https://docs.google.com/spreadsheets/d/11Y6t82BBL3vbL5yCoX7OsbPcvVO4UWc6VrOQDqKOnBI/edit?usp=sharing")
```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


